\textbf{ANALYSIS OF \\REINFORCED LEARNING \\APPLIED TO CONNNECT FOUR}

### 2022-09-21 doc/paper.tex
small stuff
typo
small changes to the paper

% title
\title{\textbf{ANALYSIS OF REINFORCED \\NEURAL NETWORKS}}

% author and supervisors
\author{\rule{8cm}{0.3mm} \\[0.5in] \textit{Adam Amanbaev, Hugo Åkerfeldt, Jonathan Hallström, Romeo Patzer} \\\\
    \small \textit{Supervisors: Ulf Backlund \& Bertil Lundberg}
}

@@

\section{Notation and Definitions}
\subsection{Notation}

>>>>

% title
\title{\textbf{ANALYSIS OF \\REINFORCED LEARNING \\APPLIED TO CONNNECT FOUR}}

% author and supervisors
\author{\rule{8cm}{0.3mm} \\[0.5in] \textit{Adam Amanbaev, Hugo Åkerfeldt, Jonathan Hallström} \\ \textit{Romeo Patzer, Alvar Edvardsson} \\\\
    \small \textit{Supervisor: Ulf Backlund}
}

@@

\section{Notation and Definitions}
\subsection{Sigma Function}
\subsection{Vector}
\subsection{Matrix}
\subsection{Derivative}
\subsection{Gradient}
